Figure 7 - heterodimer

### 2024-07-09 ms_figure_7_heterodimer.Rmd
Add genome logfc plot (Fig 7)

---
title: "Figure 6 - heterodimer"
author: "Charlotte Soneson, Michael Stadler, Merle Skribbe"
date: "`r Sys.Date()`"
output: 
    html_document:
        theme: united
        toc: true
        toc_float: true
        code_folding: hide
params:
    rds500: "data/ipms_500_sce.rds"
    rdsrnaseq_del: "data/rnaseq_del.rds"
    rdsrnaseq_ko: "data/rnaseq_ko.rds"
    dist_from_ne: "data/Fig6_lacR_quantification_distance_radius.txt"
    gtf: "reference/Schizosaccharomyces_pombe.ASM294v2.55.gtf"
    idmap: "data/id_mapping_table.txt"
    rnatracks_ko: "data/genome_browser_tracks_rnaseq_ko.csv.gz"
    chiptracks_ko: "data/genome_browser_tracks_chipseq_ko.csv.gz"
---

@@

# Figure 6

@@

@@

    scale_fill_manual(values = c(wt = "black", "ntu1\U141E" = main_colors[5], 
                                 "ntu2\U141E" = main_colors[1])) + 

@@

```{r Fig6}
#| fig.width: 13
#| fig.height: 14
#| warning: false

fig6b <- ggdraw() + 
    draw_image("schematics/Fig6B_Nattou_protein_domains_cartoon_Arial.png")
fig6e <- ggdraw() + 
    draw_image("schematics/Fig6E_Nattou_lacR_cartoon_images_Arial.png")
fig6f <- ggdraw() + 
    draw_image("schematics/Fig6F_Nattou_lacR_microscopy_images_Arial.png")

fig6c <- wrap_plots(maplots, ncol = 1) | corrplot[[1]]

cowplot::plot_grid(
    cowplot::plot_grid(
        gg_ipdimer, 
        fig6c,
        nrow = 1, 
        rel_widths = c(1, 2), 
        labels = c("A", "C"),
        align = "h", axis = "bt"
    ),
    cowplot::plot_grid(
        fig6b, 
        gcov,
        rel_widths = c(1, 1),
        labels = c("B", "D")
    ),
    cowplot::plot_grid(
        fig6e,
        NULL,
        fig6f,
        NULL,
        p_zone + theme(legend.position = "top"), 
        labels = c("E", "", "F", "", "G"),
        # rel_widths = c(7.65, 0.5, 1.45, 0.5, 9)
        rel_widths = c(6, 0.75, 1.2, 0.75, 10.4), nrow = 1
    ), 
    ncol = 1
)
```

@@

```{r suppFig6-chip}
#| warning: false
#| message: false

@@

```{r suppFig6}
#| fig.width: 13
#| fig.height: 9
#| warning: false

figs6a <- ggdraw() + 
    draw_image("schematics/FigS6A_Nattou_AF2_fl_Arial.png")

cowplot::plot_grid(
    cowplot::plot_grid(
        figs6a, 
        NULL,
        p_rel_dis,
        nrow = 1, 
        rel_widths = c(1.55, 0.25, 1.45), 
        labels = c("A", "", "B")
    ),
    cowplot::plot_grid(
        genomeplot_tpm,
        gcovdel,
        # maplots$ID83delTMD,
        nrow = 1, 
        rel_widths = c(1.2, 1),
        labels = c("C", "D")
    ),
    ncol = 1, rel_heights = c(1, 1)
)
```

>>>>

---
title: "Figure 7 - heterodimer"
author: "Charlotte Soneson, Michael Stadler, Merle Skribbe"
date: "`r Sys.Date()`"
output: 
    html_document:
        theme: united
        toc: true
        toc_float: true
        code_folding: hide
params:
    rds500: "data/ipms_500_sce.rds"
    rdsrnaseq_del: "data/rnaseq_del.rds"
    rdsrnaseq_ko: "data/rnaseq_ko.rds"
    dist_from_ne: "data/Fig7_lacR_quantification_distance_radius.txt"
    gtf: "reference/Schizosaccharomyces_pombe.ASM294v2.55.gtf"
    idmap: "data/id_mapping_table.txt"
    rnatracks_ko: "data/genome_browser_tracks_rnaseq_ko.csv.gz"
    chiptracks_ko: "data/genome_browser_tracks_chipseq_ko.csv.gz"
---

@@

# Figure 7

@@

```{r rnaseq-genomeplot}

## Add information about gene location to result lists
genepos <- rowRanges(dds)
mcols(genepos) <- NULL
genepos <- as.data.frame(genepos)
resList <- lapply(resList, function(rl) {
    stopifnot(rownames(rl) == rownames(genepos))
    cbind(rl, genepos) |>
        as.data.frame() |>
        tibble::rownames_to_column("gene")
})

## Subset to region of interest
chrom <- genepos["tna1", "seqnames"]
startpos <- genepos["tna1", "start"]
endpos <- genepos["tna1", "end"]
windowsize <- 30000

resListToPlot <- lapply(resList, function(rl) {
    rl |> dplyr::filter(seqnames == chrom & 
                            start > startpos - windowsize & 
                            end < endpos + windowsize)
})
plotList <- lapply(names(resListToPlot), function(nm) {
    ggplot(resListToPlot[[nm]], 
           aes(x = start, y = log2FoldChange, 
               color = abs(log2FoldChange) > 3 & padj < 0.001)) + 
        geom_rect(aes(xmin = endpos, xmax = startpos, ymin = -Inf, ymax = Inf),
                  color = lighten(main_colors[4], amount = 0.6), fill = NA,
                  alpha = 0.1, show.legend = FALSE) + 
        geom_point(alpha = 0.6, size = 2) + 
        scale_color_manual(values = c(`FALSE` = "grey50", 
                                      `TRUE` = main_colors[4])) + 
        geom_text_repel(aes(label = ifelse(abs(log2FoldChange) > 3 & padj < 0.001,
                                           as.character(gene), "")),
                        size = 2.5, max.overlaps = 30, force = 10) + 
        scale_x_continuous(labels = scales::label_number(scale = 1e-6)) + 
        scale_y_continuous(limits = c(-7, 7)) + 
        labs(x = "Genome position (Mb)", y = "log2(fold-change)",
             title = paste0(nm, "\U141E")) + 
        theme_cowplot() + 
        theme(legend.position = "none",
              plot.title = element_text(face = "italic"))
})
genomeplot <- cowplot::plot_grid(plotlist = plotList, ncol = 1)
```

@@

    scale_fill_manual(values = c(wt = lighten("black", amount = 0.4), 
                                 "ntu1\U141E" = lighten(main_colors[5], amount = 0.4), 
                                 "ntu2\U141E" = lighten(main_colors[1], amount = 0.4))) + 

@@

```{r Fig7}
#| fig.width: 13
#| fig.height: 14
#| warning: false

fig7b <- ggdraw() + 
    draw_image("schematics/Fig7B_Nattou_protein_domains_cartoon_Arial.png")
fig7e <- ggdraw() + 
    draw_image("schematics/Fig7E_Nattou_lacR_cartoon_images_Arial.png")
fig7f <- ggdraw() + 
    draw_image("schematics/Fig7F_Nattou_lacR_microscopy_images_Arial.png")

fig7c <- wrap_plots(maplots, ncol = 1) | corrplot[[1]]

cowplot::plot_grid(
    cowplot::plot_grid(
        gg_ipdimer, 
        fig7c,
        nrow = 1, 
        rel_widths = c(1, 2), 
        labels = c("A", "C"),
        align = "h", axis = "bt"
    ),
    cowplot::plot_grid(
        fig7b, 
        gcov,
        rel_widths = c(1, 1),
        labels = c("B", "D")
    ),
    cowplot::plot_grid(
        fig7e,
        NULL,
        fig7f,
        NULL,
        p_zone + theme(legend.position = "top"), 
        labels = c("E", "", "F", "", "G"),
        # rel_widths = c(7.65, 0.5, 1.45, 0.5, 9)
        rel_widths = c(6, 0.75, 1.2, 0.75, 10.4), nrow = 1
    ), 
    ncol = 1
)
```

@@

```{r suppFig7-chip}
#| warning: false
#| message: false

@@

```{r suppFig7}
#| fig.width: 13
#| fig.height: 15
#| warning: false

figs6a <- ggdraw() + 
    draw_image("schematics/FigS7A_Nattou_AF2_fl_Arial.png")

cowplot::plot_grid(
    figs6a,
    cowplot::plot_grid(
        p_rel_dis,
        genomeplot_tpm,
        nrow = 1, 
        rel_widths = c(1, 1), 
        labels = c("B", "C")
    ),
    cowplot::plot_grid(
        genomeplot,
        gcovdel,
        # maplots$ID83delTMD,
        nrow = 1, 
        rel_widths = c(1, 1),
        labels = c("C", "E")
    ),
    ncol = 1, rel_heights = c(1, 1, 1)
)
```
